---
title       : Iris dataset data analysis
subtitle    : Analyzing linear correlations of the iris dataset
author      : Francisco Sokol
job         : Software Developer - Caelum - Brazil, Sao Paulo
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides

--- .class #id 

## The iris dataset

The iris dataset is a collection of measurements gathered from 
50 flowers of 3 different species.

This dataset is bundled with R, and can be examined with the `iris` variable.

The following variables are available in the dataframe:

```{r}
names(iris)
```

---
## The iris dataset

Here is a summary of the dataframe:

```{r}
summary(iris)
```

---

## Linear correlations

When anlysing the whole dataset, there seems to be a some positive linear correlation
between Sepal and Petal Length:

```{r echo=FALSE}
iris.lm <- lm(iris$Petal.Length ~ iris$Sepal.Length)

plot(iris$Sepal.Length, iris$Petal.Length, pch=19)
abline(iris.lm, col="blue")
```

---

## Linear correlations

But when we partition the data between the three different species, we can see that
this correlantion is higher:

```{r echo=FALSE}
virginica = iris[iris$Species=="virginica",]
virginica.lm <- lm(virginica$Petal.Length ~ virginica$Sepal.Length)

setosa = iris[iris$Species=="setosa",]
setosa.lm <- lm(setosa$Petal.Length ~ setosa$Sepal.Length)

versicolor = iris[iris$Species=="versicolor",]
versicolor.lm <- lm(versicolor$Petal.Length ~ versicolor$Sepal.Length)

plot(iris$Sepal.Length, iris$Petal.Length, pch=19, col=iris$Species)
abline(virginica.lm, col="green")
abline(setosa.lm, col="black")
abline(versicolor.lm, col="red")
legend("topleft", inset=0.01, c("setosa", "versicolor", "virginica"), pch=19, 
             col=c("black", "red", "green"), title="Species")
```

